Improving content discovery through combining linked data and data mining techniques

### 2015-11-25 report/report.tex
Started some context visualisation.

An approach of generating attributes for a given resource was proposed by
Paulheim and F\:urnkranz\cite{paulheim2012unsupervised}. They defined specific
SPARQL queries and provided case study evidence for the effectiveness of
each strategy.

@@

@@

        IRI -> RDFa [label="fetch"];
        RDFa -> RDF [label="parse"];
        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Semantic web content miner}
\end{figure}

>>>>

An approach of generating attributes for a given resource was proposed by
Paulheim and F\"urnkranz\cite{paulheim2012unsupervised}. They defined specific
SPARQL queries and provided case study evidence for the effectiveness of
each strategy.

@@

Many tools such as the RDFLib\footnote{https://github.com/RDFLib/rdflib}
provide functionality for taking a URL and returning an RDF graph of all data
found when fetching the resource it represents, so this is arguably an ideal
first choice in attempting to learn something about a content item from its
IRI.

@@

        IRI -> RDFa [label="fetch"];
        RDFa -> RDF [label="parse"];
        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{Semantic web content miner\label{fig:gen-rdfa}}
\end{figure}

Figure~\ref{fig:gen-rdfa}
